# Reconstructing Data Based on the Guyot et al. 2016 Algorithm {#math-sci}

<!-- Required to number equations in HTML files -->
<script type="text/x-mathjax-config">
MathJax.Hub.Config({
  TeX: { equationNumbers: { autoNumber: "AMS" } }
});
</script>

## Mok et al. 2009 IPASS Study: Crossing Hazards

```{r, results="asis", echo=FALSE, fig.cap="Patients with unknown EGFR mutation status", out.extra="scale=0.55", fig.align='center', eval=F}
knitr::include_graphics("figure/mok.2.a.pdf")
```

<br>
<br>

```{r, fig.cap="patients who were positive for the EGFR mutation", echo=FALSE, eval=T}
knitr::include_graphics(path = "figure/mok.2.a.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Summary Statistics", warning=FALSE, message=FALSE}
source("Libraries.R")

IPD.Mok.A <- readRDS("data/IPD.Mok.A.RDS")

# rename columns 
colnames(IPD.Mok.A) <- c("time", "event", "Gefitinib")

IPD.Mok.A$Gefitinib <- ifelse(IPD.Mok.A$Gefitinib == 0, "Carboplatin", "Gefitinib")

IPD.Mok.A %>%
  tbl_summary(
    by = Gefitinib,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  modify_header(stat_by = md("**{level}**<br>N =  {n} ({style_percent(p)}%)")) %>%
  bold_labels() %>%
  modify_spanning_header(starts_with("stat_") ~ "**Gefitinib or Carboplatin-Paclitaxel**") %>% 
  add_p(test = all_continuous() ~ "t.test") %>%
  add_overall()
```

<br>
<br>

```{r echo=FALSE, fig.cap="Cox Proportional Hazards Model"}
source("Libraries.R")

IPD.Mok.A <- readRDS("data/IPD.Mok.A.RDS")

colnames(IPD.Mok.A) <- c("time", "event", "arm")

# fit coxph model
cox.model <- coxph(Surv(time, event) ~ arm, data = IPD.Mok.A) 

# format results into data frame with global p-values
cox.model %>%
  tbl_regression(
    show_single_row = arm,
    label = arm ~ "Gefitinib vs Carboplatin-Paclitaxel",
    exponentiate = TRUE) %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  italicize_levels()
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Forest Plot"}
knitr::include_graphics(path = "figure/mok.a.f.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Schoenfeld Test"}
knitr::include_graphics(path = "figure/mok.a.sch.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Weighted Log Rank Test"}
source("Libraries.R")

IPD.Mok.A <- readRDS("data/IPD.Mok.A.RDS")

DT <- setDT(IPD.Mok.A)

colnames(IPD.Mok.A) <- c("time", "event", "arm")

result <- wlr.Stat(surv=DT$time, cnsr=DT$event, trt= DT$arm, fparam=list(rho=c(0,0,1,1), gamma=c(0,1,1,0), wlr='FH(0,1)', APPLE=3))

result %>% 
  kableExtra::kable()
```

<br>
<br>

------------------------------------------------------------------------
  Rho     Gamma   Zmax     Pval     HR     hrL    hrU    hrL.bc  hrU.bc                      
-------- ------- ------- -------- ------ ------ ------- ------- -------- 
   1        0     2.768   0.004   0.682  0.521   0.893   0.511   0.903          
------------------------------------------------------------------------

\clearpage 

## Brehmer et al. 2016 Nivolumab versus Docetaxel Study: Crossing Hazards

```{r, results="asis", echo=FALSE, fig.cap="Kaplan–Meier curves for overall survival", out.extra="scale=0.55", fig.align='center', eval=F}
knitr::include_graphics("figure/brehmer.pdf")
```

<br>
<br>

```{r, fig.cap="Kaplan–Meier curves for overall survival", echo=FALSE, eval=T}
knitr::include_graphics(path = "figure/brehmer.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Summary Statistics", warning=FALSE, message=FALSE}
source("Libraries.R")

IPD.Brahmer.a <- readRDS("data/IPD.Brahmer.a.RDS")

# rename columns 
colnames(IPD.Brahmer.a) <- c("time", "event", "Nivolumab")

IPD.Brahmer.a$Nivolumab <- ifelse(IPD.Brahmer.a$Nivolumab == 0, "Docetaxel", "Nivolumab")

IPD.Brahmer.a %>%
  tbl_summary(
    by = Nivolumab,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  modify_header(stat_by = md("**{level}**<br>N =  {n} ({style_percent(p)}%)")) %>%
  bold_labels() %>%
  modify_spanning_header(starts_with("stat_") ~ "**Nivolumab vs Docetaxel**") %>% 
  add_p(test = all_continuous() ~ "t.test") %>%
  add_overall()
```

<br>
<br>

```{r echo=FALSE, fig.cap="Cox Proportional Hazards Model"}
source("Libraries.R")

IPD.Brahmer.a <- readRDS("data/IPD.Brahmer.a.RDS")

colnames(IPD.Brahmer.a) <- c("time", "event", "arm")

# fit coxph model
cox.model <- coxph(Surv(time, event) ~ arm, data = IPD.Brahmer.a) 

# format results into data frame with global p-values
cox.model %>%
  tbl_regression(
    show_single_row = arm,
    label = arm ~ "Nivolumab vs Docetaxel",
    exponentiate = TRUE) %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

```{r, echo=FALSE, fig.cap="Forest Plot"}
knitr::include_graphics(path = "figure/brahmer.f.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Schoenfeld Test"}
knitr::include_graphics(path = "figure/brahmer.sch.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Weighted Log Rank Test"}
source("Libraries.R")

IPD.Brahmer.a <- readRDS("data/IPD.Brahmer.a.RDS")

DT <- setDT(IPD.Brahmer.a)

colnames(IPD.Brahmer.a) <- c("time", "event", "arm")

result <- wlr.Stat(surv=DT$time, cnsr=DT$event, trt= DT$arm, fparam=list(rho=c(0,0,1,1), gamma=c(0,1,1,0), wlr='FH(0,1)', APPLE=3))

result %>% 
  kableExtra::kable()
```

<br>
<br>

------------------------------------------------------------------------
  Rho     Gamma   Zmax     Pval     HR     hrL    hrU    hrL.bc  hrU.bc                      
-------- ------- ------- -------- ------ ------ ------- ------- -------- 
   1        1     1.083   0.4000   0.833  0.599   1.159   0.655   1.042          
------------------------------------------------------------------------

\clearpage 

## Mok et al. 2009 IPASS Study: Dimishing Treatment Effect

```{r, results="asis", echo=FALSE, fig.cap="Patients with unknown EGFR mutation status", out.extra="scale=0.55", fig.align='center', eval=F}
knitr::include_graphics("figure/mok.2.c.pdf")
```

<br>
<br>

```{r, fig.cap="Patients with unknown EGFR mutation status", echo=FALSE, eval=T}
knitr::include_graphics(path = "figure/mok.2.c.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Summary Statistics", warning=FALSE, message=FALSE}
source("Libraries.R")

IPD.Mok.C <- readRDS("data/IPD.Mok.C.RDS")

colnames(IPD.Mok.C) <- c("time", "event", "Gefitinib")

IPD.Mok.C$Gefitinib <- ifelse(IPD.Mok.C$Gefitinib == 0, "Carboplatin", "Gefitinib")

IPD.Mok.C %>%
  tbl_summary(
    by = Gefitinib,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  modify_header(stat_by = md("**{level}**<br>N =  {n} ({style_percent(p)}%)")) %>%
  bold_labels() %>%
  modify_spanning_header(starts_with("stat_") ~ "**Gefitinib vs Carboplatin-Paclitaxel**") %>% 
  add_p(test = all_continuous() ~ "t.test") %>%
  add_overall()
```

<br>
<br>

```{r echo=FALSE, fig.cap="Cox Proportional Hazards Model"}
source("Libraries.R")

IPD.Mok.C <- readRDS("data/IPD.Mok.C.RDS")

colnames(IPD.Mok.A) <- c("time", "event", "arm")

# fit coxph model
cox.model <- coxph(Surv(time, event) ~ arm, data = IPD.Mok.C) 

# format results into data frame with global p-values
cox.model %>%
  tbl_regression(
    show_single_row = arm,
    label = arm ~ "Gefitinib vs Carboplatin-Paclitaxel",
    exponentiate = TRUE) %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  italicize_levels()
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Forest Plot"}
knitr::include_graphics(path = "figure/mok.c.f.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Schoenfeld Test"}
knitr::include_graphics(path = "figure/mok.c.sch.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Weighted Log Rank Test"}
source("Libraries.R")

IPD.Mok.C <- readRDS("data/IPD.Mok.C.RDS")

DT <- setDT(IPD.Mok.C)

colnames(IPD.Mok.C) <- c("time", "event", "arm")

result <- wlr.Stat(surv=DT$time, cnsr=DT$event, trt= DT$arm, fparam=list(rho=c(0,0,1,1), gamma=c(0,1,1,0), wlr='FH(0,1)', APPLE=3))

result %>% 
  kableExtra::kable()
```

<br>
<br>

------------------------------------------------------------------------
  Rho     Gamma   Zmax     Pval     HR     hrL    hrU    hrL.bc  hrU.bc                      
-------- ------- ------- -------- ------ ------ ------- ------- -------- 
   1        0     5.998   0.000   0.081  0.028   0.232   0.026   0.302          
------------------------------------------------------------------------

\clearpage 

## Ohtsu et al. 2011 AVAGAST Study: Dimishing Treatment Effect

```{r, results="asis", echo=FALSE, fig.cap="Patients in the intention-to-treat population", out.extra="scale=0.55", fig.align='center', eval=F}
knitr::include_graphics("figure/ohtsu.pdf")
```

<br>
<br>

```{r, fig.cap="Patients in the intention-to-treat population", echo=FALSE, eval=T}
knitr::include_graphics(path = "figure/ohtsu.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Summary Statistics", warning=FALSE, message=FALSE}
source("Libraries.R")

IPD.Ohtsu <- readRDS("data/IPD.Ohtsu.RDS")

colnames(IPD.Ohtsu) <- c("time", "event", "Bevacizumab")

IPD.Ohtsu$Bevacizumab <- ifelse(IPD.Ohtsu$Bevacizumab == 0, "Placebo", "Bevacizumab")

IPD.Ohtsu %>%
  tbl_summary(
    by = Bevacizumab,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  modify_header(stat_by = md("**{level}**<br>N =  {n} ({style_percent(p)}%)")) %>%
  bold_labels() %>%
  modify_spanning_header(starts_with("stat_") ~ "**Bevacizumab in Combination With Chemotherapy**") %>% 
  add_p(test = all_continuous() ~ "t.test") %>%
  add_overall()
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Cox Proportional Hazards Model"}
source("Libraries.R")

IPD.Ohtsu <- readRDS("data/IPD.Ohtsu.RDS")

colnames(IPD.Ohtsu) <- c("time", "event", "arm")

# fit coxph model
cox.model <- coxph(Surv(time, event) ~ arm, data = IPD.Ohtsu) 

# format results into data frame with global p-values
cox.model %>%
  tbl_regression(
    show_single_row = arm,
    label = arm ~ "Bevacizumab vs Placebo",
    exponentiate = TRUE) %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  italicize_levels()

```

<br>
<br>

```{r, echo=FALSE, fig.cap="Forest Plot"}
knitr::include_graphics(path = "figure/ohtsu.f.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Schoenfeld Test"}
knitr::include_graphics(path = "figure/ohtsu.sch.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Weighted Log Rank Test"}
source("Libraries.R")

IPD.Ohtsu <- readRDS("data/IPD.Ohtsu.RDS")

DT <- setDT(IPD.Ohtsu)

colnames(IPD.Ohtsu) <- c("time", "event", "arm")

result <- wlr.Stat(surv=DT$time, cnsr=DT$event, trt= DT$arm, fparam=list(rho=c(0,0,1,1), gamma=c(0,1,1,0), wlr='FH(0,1)', APPLE=3))

result %>% 
  kableExtra::kable()
```

<br>
<br>

------------------------------------------------------------------------
  Rho     Gamma   Zmax     Pval     HR     hrL    hrU    hrL.bc  hrU.bc                      
-------- ------- ------- -------- ------ ------ ------- ------- -------- 
   0        1     1.831   0.000   0.763  0.573   1.017   0.687   0.931          
------------------------------------------------------------------------

\clearpage 

## Ascierto et al. 2017 The Ipilimumab Study: Delayed Treatment Effect

```{r, results="asis", echo=FALSE, fig.cap="Patients in the intention-to-treat population", out.extra="scale=0.55", fig.align='center', eval=F}
knitr::include_graphics("figure/ascierto.pdf")
```

<br>
<br>

```{r, fig.cap="Patients in the intention-to-treat population", echo=FALSE, eval=T}
knitr::include_graphics(path = "figure/ascierto.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Summary Statistics", warning=FALSE, message=FALSE}
source("Libraries.R")

IPD.ascierto.2.a <- readRDS("data/IPD.ascierto.2.a.RDS")

# rename columns 
colnames(IPD.ascierto.2.a) <- c("time", "event", "10mg")

IPD.ascierto.2.a$`10mg` <- ifelse(IPD.ascierto.2.a$`10mg` == 0, "3mg", "10mg")

IPD.ascierto.2.a %>%
  tbl_summary(
    by = `10mg`,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  modify_header(stat_by = md("**{level}**<br>N =  {n} ({style_percent(p)}%)")) %>%
  bold_labels() %>%
  modify_spanning_header(starts_with("stat_") ~ "**Ipilimumab 10 mg/kg versus ipilimumab 3 mg/kg**") %>% 
  add_p(test = all_continuous() ~ "t.test") %>%
  add_overall()
```

<br>
<br>

```{r echo=FALSE, fig.cap="Cox Proportional Hazards Model"}
source("Libraries.R")
IPD.ascierto.2.a <- readRDS("data/IPD.ascierto.2.a.RDS")

colnames(IPD.ascierto.2.a) <- c("time", "event", "arm")

# fit coxph model
cox.model <- coxph(Surv(time, event) ~ arm, data = IPD.ascierto.2.a) 

# format results into data frame with global p-values
cox.model %>%
  tbl_regression(
    show_single_row = arm,
    label = arm ~ "10mg vs 3mg",
    exponentiate = TRUE) %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  italicize_levels()
```

```{r, echo=FALSE, fig.cap="Forest Plot"}
knitr::include_graphics(path = "figure/ascierto.f.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Schoenfeld Test"}
knitr::include_graphics(path = "figure/preview.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Weighted Log Rank Test"}
source("Libraries.R")

IPD.ascierto.2.a <- readRDS("data/IPD.ascierto.2.a.RDS")

DT <- setDT(IPD.ascierto.2.a)

colnames(IPD.ascierto.2.a) <- c("time", "event", "arm")

result <- wlr.Stat(surv=DT$time, cnsr=DT$event, trt= DT$arm, fparam=list(rho=c(0,0,1,1), gamma=c(0,1,1,0), wlr='FH(0,1)', APPLE=3))

result %>% 
  kableExtra::kable()
```

<br>
<br>

------------------------------------------------------------------------
  Rho     Gamma   Zmax     Pval     HR     hrL    hrU    hrL.bc  hrU.bc                      
-------- ------- ------- -------- ------ ------ ------- ------- -------- 
   0        1     8.471   0.000   0.238  0.190   0.299   0.195   0.291          
------------------------------------------------------------------------

\clearpage 

## Rittermeyer et al. 2017 The OAK Study: Delayed Treatment Effect

```{r, results="asis", echo=FALSE, fig.cap="Patients in the WT population", out.extra="scale=0.55", fig.align='center', eval=F}
knitr::include_graphics("figure/reck.pdf")
```

<br>
<br>

```{r, fig.cap="Patients in the WT population", echo=FALSE, eval=T}
knitr::include_graphics(path = "figure/Rittmeyer.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Summary Statistics", warning=FALSE, message=FALSE}
source("Libraries.R")

IPD.Rittmeyer <- readRDS("data/IPD.Rittmeyer.RDS")

# rename columns 
colnames(IPD.Rittmeyer) <- c("time", "event", "Atezolizumab")

IPD.Rittmeyer$Atezolizumab <- ifelse(IPD.Rittmeyer$Atezolizumab == 0, "Docetaxel", "Atezolizumab")

IPD.Rittmeyer %>%
  tbl_summary(
    by = Atezolizumab,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} / {N} ({p}%)")
  ) %>%
  modify_header(stat_by = md("**{level}**<br>N =  {n} ({style_percent(p)}%)")) %>%
  bold_labels() %>%
  modify_spanning_header(starts_with("stat_") ~ "**Atezolizumab versus Docetaxel**") %>% 
  add_p(test = all_continuous() ~ "t.test") %>%
  add_overall()
```

<br>
<br>

```{r echo=FALSE, fig.cap="Cox Proportional Hazards Model"}
source("Libraries.R")

IPD.Rittmeyer <- readRDS("data/IPD.Rittmeyer.RDS")

colnames(IPD.Rittmeyer) <- c("time", "event", "arm")

# fit coxph model
cox.model <- coxph(Surv(time, event) ~ arm, data = IPD.Rittmeyer) 

# format results into data frame with global p-values
cox.model %>%
  tbl_regression(
    show_single_row = arm,
    label = arm ~ "Atezolizumab versus Docetaxel",
    exponentiate = TRUE) %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  italicize_levels()
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Forest Plot"}
knitr::include_graphics(path = "figure/ritt.f.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Schoenfeld Test"}
knitr::include_graphics(path = "figure/riiter.sch.svg")
```

<br>
<br>

```{r, echo=FALSE, fig.cap="Weighted Log Rank Test"}
source("Libraries.R")

IPD.Rittmeyer <- readRDS("data/IPD.Rittmeyer.RDS")

DT <- setDT(IPD.Rittmeyer)

colnames(IPD.Rittmeyer) <- c("time", "event", "arm")

result <- wlr.Stat(surv=DT$time, cnsr=DT$event, trt= DT$arm, fparam=list(rho=c(0,0,1,1), gamma=c(0,1,1,0), wlr='FH(0,1)', APPLE=3))

result %>% 
  kableExtra::kable()
```

<br>
<br>

------------------------------------------------------------------------
  Rho     Gamma   Zmax     Pval     HR     hrL    hrU    hrL.bc  hrU.bc                      
-------- ------- ------- -------- ------ ------ ------- ------- -------- 
   1        0     2.041   0.000   0.761  0.586   0.989   0.561   1.005         
------------------------------------------------------------------------

## Math

\TeX\ is the best way to typeset mathematics. Donald Knuth designed \TeX\ when he got frustrated at how long it was taking the typesetters to finish his book, which contained a lot of mathematics.  One nice feature of _R Markdown_ is its ability to read LaTeX code directly.

If you are doing a thesis that will involve lots of math, you will want to read the following section which has been commented out. If you're not going to use math, skip over or delete this next commented section.


<!-- MATH and PHYSICS majors: Uncomment the following section -->
<!--
$$\sum_{j=1}^n (\delta\theta_j)^2 \leq {{\beta_i^2}\over{\delta_i^2 + \rho_i^2}}
\left[ 2\rho_i^2 + {\delta_i^2\beta_i^2\over{\delta_i^2 + \rho_i^2}} \right] \equiv \omega_i^2
$$

From Informational Dynamics, we have the following (Dave Braden):

After _n_ such encounters the posterior density for $\theta$ is

$$
\pi(\theta|X_1< y_1,\dots,X_n<y_n) \varpropto \pi(\theta) \prod_{i=1}^n\int_{-\infty}^{y_i}
   \exp\left(-{(x-\theta)^2\over{2\sigma^2}}\right)\ dx
$$

Another equation:

$$\det\left|\,\begin{matrix}%
c_0&c_1\hfill&c_2\hfill&\ldots&c_n\hfill\cr
c_1&c_2\hfill&c_3\hfill&\ldots&c_{n+1}\hfill\cr
c_2&c_3\hfill&c_4\hfill&\ldots&c_{n+2}\hfill\cr
\,\vdots\hfill&\,\vdots\hfill&
  \,\vdots\hfill&&\,\vdots\hfill\cr
c_n&c_{n+1}\hfill&c_{n+2}\hfill&\ldots&c_{2n}\hfill\cr
\end{matrix}\right|>0$$


Lapidus and Pindar, Numerical Solution of Partial Differential Equations in Science and
Engineering.  Page 54

$$
\int_t\left\{\sum_{j=1}^3 T_j \left({d\phi_j\over dt}+k\phi_j\right)-kT_e\right\}w_i(t)\ dt=0,
   \qquad\quad i=1,2,3.
$$

L\&P  Galerkin method weighting functions.  Page 55

$$
\sum_{j=1}^3 T_j\int_0^1\left\{{d\phi_j\over dt} + k\phi_j\right\} \phi_i\ dt
   = \int_{0}^1k\,T_e\phi_idt, \qquad i=1,2,3 $$

Another L\&P (p145)

$$
\int_{-1}^1\!\int_{-1}^1\!\int_{-1}^1 f\big(\xi,\eta,\zeta\big)
   = \sum_{k=1}^n\sum_{j=1}^n\sum_{i=1}^n w_i w_j w_k f\big( \xi,\eta,\zeta\big).
$$

Another L\&P (p126)

$$
\int_{A_e} (\,\cdot\,) dx dy = \int_{-1}^1\!\int_{-1}^1 (\,\cdot\,) \det[J] d\xi d\eta.
$$
-->

## Chemistry 101: Symbols

Chemical formulas will look best if they are not italicized. Get around math mode's automatic italicizing in LaTeX by using the argument `$\mathrm{formula here}$`, with your formula inside the curly brackets.  (Notice the use of the backticks here which enclose text that acts as code.)

So, $\mathrm{Fe_2^{2+}Cr_2O_4}$ is written `$\mathrm{Fe_2^{2+}Cr_2O_4}$`.

<!--
The \noindent command below does what you'd expect:  it forces the current line/paragraph to not indent. This was done here to match the format of the LaTeX thesis PDF.
-->

\noindent Exponent or Superscript: $\mathrm{O^-}$

\noindent Subscript: $\mathrm{CH_4}$

To stack numbers or letters as in $\mathrm{Fe_2^{2+}}$, the subscript is defined first, and then the superscript is defined.

\noindent Bullet: CuCl $\bullet$ $\mathrm{7H_{2}O}$


\noindent Delta: $\Delta$

\noindent Reaction Arrows: $\longrightarrow$ or  $\xrightarrow{solution}$

\noindent Resonance Arrows: $\leftrightarrow$

\noindent Reversible Reaction Arrows: $\rightleftharpoons$

### Typesetting reactions

You may wish to put your reaction in an equation environment, which means that LaTeX will place the reaction where it fits and will number the equations for you. 

\begin{equation}
  \mathrm{C_6H_{12}O_6  + 6O_2} \longrightarrow \mathrm{6CO_2 + 6H_2O}
  (\#eq:reaction)
\end{equation}

We can reference this combustion of glucose reaction via Equation \@ref(eq:reaction).

### Other examples of reactions

$\mathrm{NH_4Cl_{(s)}}$ $\rightleftharpoons$ $\mathrm{NH_{3(g)}+HCl_{(g)}}$

\noindent $\mathrm{MeCH_2Br + Mg}$ $\xrightarrow[below]{above}$ $\mathrm{MeCH_2\bullet Mg \bullet Br}$

## Physics

Many of the symbols you will need can be found on the math page <https://web.reed.edu/cis/help/latex/math.html> and the Comprehensive LaTeX Symbol Guide (<https://mirror.utexas.edu/ctan/info/symbols/comprehensive/symbols-letter.pdf>).

## Biology

You will probably find the resources at <https://www.lecb.ncifcrf.gov/~toms/latex.html> helpful, particularly the links to bsts for various journals. You may also be interested in TeXShade for nucleotide typesetting (<https://homepages.uni-tuebingen.de/beitz/txe.html>).  Be sure to read the proceeding chapter on graphics and tables.

